%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used for an ATLAS note.
%-------------------------------------------------------------------------------

% Title
\AtlasTitle{Search for $t\bar tH/A \rightarrow \tttt$ production in a final state with one lepton or two opposite-sign leptons using the full Run 2 $pp$ collisions data at $\sqrt{s} = 13$ \TeV}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.9}

% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
  This note presents a search for a new heavy Higgs-boson in the process $t\bar tH/A \rightarrow \tttt$  using an integrated luminosity of 139 fb$^{-1}$ of proton-proton collision data at a centre-of-mass energy of 13 TeV collected by the ATLAS detector at the LHC. 
Events are selected if they contain exactly one lepton or two opposite-sign lepton pairs (electrons or muons).

The signal-enriched regions are defined by exploiting the high jet and b-jet multiplicities.  
The signal is then separated from the background through a multivariate discriminant, and dedicated signal-depleted regions are used to constrain the dominant backgrounds. No significant excess of events over Standard Model expectation is observed.  The results are interpreted in the context of the two-Higgs-doublet model, and  observed(expected) 95\% CL upper limits on the cross-section times branching ratio of  $H/A \rightarrow \ttbar$  have been  estimated to range between 40.8(25.7) fb and 7.1(6.1) fb  for a heavy Higgs boson mass  between 400~\GeV~and 1000~\GeV, respectively. }

% Author - this does not work with revtex (add it after \begin{document})
%\author{The ATLAS Collaboration}

 %Authors and list of contributors to the analysis
% \AtlasAuthorContributor also adds the name to the author list
 %Include package latex/atlascontribute to use this
% Use authblk package if there are multiple authors, which is included by latex/atlascontribute

% \usepackage{latex/atlascontribute}
% \usepackage{authblk}
% Use the following 3 lines to have all institutes on one line
 \makeatletter
 \renewcommand\AB@affilsepx{, \protect\Affilfont}
 \makeatother
 \renewcommand\Authands{, } % avoid ``. and'' for last author
 \renewcommand\Affilfont{\itshape\small} % affiliation formatting
 
 
 \AtlasAuthorContributor{S. Berlendis}{a}{1LOS channel. Software development and maintenance.}
 \AtlasAuthorContributor{P. Berta}{b}{1LOS channel. Analysis contact, fit studies.}
 \AtlasAuthorContributor{C. Birch-Sykes}{c}{1LOS channel. MVA analysis, graph NN for signal background discrimination.}
 \AtlasAuthorContributor{C. Chauhan}{b}{1LOS channel. Main analyzer, validation in data of MVA discriminants, general data/MC comparison, fit studies, ntuple production.}
 \AtlasAuthorContributor{J. Guo}{e}{1LOS channel. Supervision of Lining Mao.}
 \AtlasAuthorContributor{S. Huang}{d}{SSML channel. Charge flip background estimation.}
 \AtlasAuthorContributor{K. Johns}{a}{1LOS channel. Contact editor, supervision of Rachel Lindley.}
 \AtlasAuthorContributor{Q. Jiang}{d}{1LOS channel. Validation of the sgluon samples.}
 \AtlasAuthorContributor{A. Juste Rozas}{e}{1LOS channel. Supervision of Anil Sonay.}
 \AtlasAuthorContributor{R. Lindley}{a}{1LOS channel. Main analyzer, sensitivity estimate, quark/gluon tagging for MVA analysis, fit studies.}
 \AtlasAuthorContributor{L. Mao}{e}{1LOS channel. Main analyzer, fit studies, combination with SSML, sgluon interpretation.}
 \AtlasAuthorContributor{N. Orlando}{e}{1LOS channel. Analysis contact, analysis strategy.}
 \AtlasAuthorContributor{D. Paredes Hernandez}{d}{Analysis contact, contact editor, software development and maintenance, ntuples production, student supervision, MC requests.}
 \AtlasAuthorContributor{R. Peters}{c}{1LOS channel. Supervision of Callum Birch Sykes.}
 \AtlasAuthorContributor{J. Qian}{f}{SSML channel. Supervision of Meng-Ju Tsai.}
 \AtlasAuthorContributor{Y. Qin}{c}{1LOS channel. Contact Editor, analysis strategy, supervision of Callum Birch Sykes.}
 \AtlasAuthorContributor{D. Scheirich}{b}{1LOS channel, data/MC comparison.}
 \AtlasAuthorContributor{A. Sonay}{e}{1LOS channel. Main analyzer, MVA analysis, NN based background estimation, full 1LOS analysis chain and software preparation.}
 \AtlasAuthorContributor{K. C. Tam}{d}{1LOS channel. Main analyzer, MVA analysis and optimisation, tt+HF data-driven correction.}
 \AtlasAuthorContributor{M. Tsai}{f}{SSML channel. SM BDT, BSM BDT, Signal region optimisation, statistical interpretation.}
 \AtlasAuthorContributor{Y. Tu}{d}{SSML channel. Student supervision.}
 \AtlasAuthorContributor{C. Vernieri}{g}{SSML channel. Postdoc supervision, supervision of Zhi Zheng.}
 \AtlasAuthorContributor{Z. Zheng}{g}{SSML channel. ttW studies, systematics for fakes background.}

 
% \author[a]{University of Arizona}
 %\author[a]{DESY}
 %\author[b]{Third Author}
 \affil[a]{University of Arizona}
 \affil[b]{Charles University, Prague}
 \affil[c]{University of Manchester}
\affil[d]{University of Hong Kong}
\affil[e]{IFAE}
\affil[f]{University of Michigan}
\affil[g]{SLAC}
\affil[e]{Shanghai Jiao Tong University}

% If a special author list should be indicated via a link use the following code:
% Include the two lines below if you do not use atlasstyle:
% \usepackage[marginal,hang]{footmisc}
% \setlength{\footnotemargin}{0.5em}
%% Use the following lines in all cases:
% \usepackage{authblk}
% \author{The ATLAS Collaboration%
% \thanks{The full author list can be found at:\newline
%   \url{https://atlas.web.cern.ch/Atlas/PUBNOTES/ATL-PHYS-PUB-2016-007/authorlist.pdf}}
% }

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{ANA-EXOT-2022-13}

% ATLAS note number. Can be an COM, INT, PUB or CONF note
\AtlasNote{ANA-EXOT-2022-13-INT1}
