% !TEX root = ../main.tex

\chapter{Summary and Outlook}

A search for heavy resonances decaying into top-quark pairs in the four-tops final state is performed 
using the full Run~2 dataset collected by the ATLAS experiment at $\sqrt{s}=13~\mathrm{TeV}$, 
corresponding to an integrated luminosity of 139~fb$^{-1}$. 
Events with one lepton or two opposite-sign leptons and high jet multiplicities are analysed. 
The dominant $t\bar{t}+\text{jets}$ background is controlled using a combination of 
data-driven normalisation and multidimensional kinematic corrections based on neural networks. 
Signal sensitivity is further enhanced through the use of a mass-parameterised Graph Neural Network.
No significant deviation from the Standard Model prediction is observed. 
Upper limits at 95\% confidence level are set on 
$\sigma(pp \to t\bar{t}H/A)\times \mathcal{B}(H/A \to t\bar{t})$ 
for resonance masses between 400 and 1000~GeV. 
The limits are 14~fb (5.0~fb) at 400~GeV (1000~GeV), respectively, 
and are obtained from a combination with same-sign and multilepton channels.
The resulting limits improve upon previous results by up to 19\%. 
The results are also interpreted in the context of colour-octet scalar ($S_8$) production, 
excluding $S_8$ masses up to 1.3~TeV. 
Projections to the HL-LHC demonstrate that the sensitivity to heavy resonances 
will be significantly extended, with cross-section limits below 1~fb achievable 
for masses above 1~TeV and discovery-level sensitivity reachable for benchmark scenarios.

To further exploit the physics potential of four-tops production, 
a dedicated reconstruction and unfolding framework is developed for differential measurements 
in the same-sign dilepton channel. 
A novel event reconstruction strategy is introduced using the blended hypergraph-graph framework HyPER, 
which enables a consistent assignment of reconstructed objects to the four top-quark decay chains. 
The reconstruction is complemented by neutrino inference techniques, 
including both analytic solutions and generative $\nu^2$-Flows, 
allowing the full kinematics of the four-tops system to be reconstructed.
Based on this reconstruction, a profile likelihood unfolding approach is implemented 
to extract differential cross sections at parton level. 
The unfolding is formulated within a unified likelihood framework with independent signal-strength parameters per bin, 
and is stabilised through regularisation. 
Extensive validation studies demonstrate that the method provides stable and unbiased results, 
establishing a robust foundation for future differential measurements in Run~3 data.

In parallel, contributions to the ATLAS muon spectrometer have been made through work on Resistive Plate Chambers (RPCs). 
This includes the development of automated monitoring tools based on Detector Control System data, 
as well as participation in studies related to the Phase-II RPC upgrade. 
In addition, an independent detector R\&D study has been carried out to investigate improvements 
in large-area glass RPC chamber design.

The sensitivity of the search presented in this thesis, particularly in the single-lepton and opposite-sign dilepton channels, is primarily limited by the large $t\bar{t}+\mathrm{jets}$ background. 
Improvements in background modelling and signal--background discrimination are therefore expected to yield significant gains in sensitivity. 
Advances in data-driven techniques and machine-learning-based approaches may provide a more accurate description of the heavy-flavour composition and kinematic properties of the background.

Projection studies for the HL-LHC show that the increased integrated luminosity will substantially enhance the discovery potential for new physics in four-tops final states. 
However, the sensitivity is expected to approach a regime where systematic uncertainties become dominant. 
Continued progress will therefore rely on improved theoretical modelling and more precise detector calibration. 
Reducing modelling uncertainties through higher-precision simulations, as well as improving jet reconstruction and calibration to constrain jet energy scale and resolution uncertainties, will play a crucial role.

Developments in event reconstruction techniques are expected to further enhance both the physics reach and the interpretability of four-tops events. 
More advanced machine-learning-based approaches, capable of performing object assignment and neutrino reconstruction in a unified framework, may provide a more complete description of the event topology. 
Improvements in $b$-tagging performance, for instance through next-generation algorithms such as the GN2 tagger and upgrades to the tracking detectors, are also expected to significantly enhance the identification efficiency of heavy-flavour jets, which are central to four-tops signatures.

Finally, the differential measurement framework developed in this thesis opens the possibility to probe the detailed kinematic structure of four-tops production. 
Such measurements are expected to provide enhanced sensitivity to new physics effects, particularly in the high-energy tails of observables, and offer a complementary approach to inclusive searches in the HL-LHC era.