\subsection{Target} 

This search targets the production of a heavy Higgs boson in association with two top quarks, with Higgs boson decaying into a pair of top quarks.  
The mass range under study is $m_H\in [400,1000]$~\GeV. 

The search presented in this note exploits an experimental topology featuring one lepton (1L), electron or muon, or two leptons with opposite charge (opposite-sign 2LOS).

The search is based on a similar publication~\cite{ATLAS:2021kqb} and incorporates several developments, 
ranging from updated objects definition, improved multivariate analysis strategy and 
refined background model. This search targets unblinding approval by end of March 2023, group approval in middle Fall and release of a paper before the end of 2023. 

\subsection{Context and Motivation} 

This search looks for a heavy Higgs boson in association with two top quarks with Higgs boson decaying into a pair of top quarks. In 2HDM's scenarios this signature is 
compelling as it allows to uniquely access a parameter space and mass region currently unprobed at the LHC, with the exception of the gluon-fusion heavy Higgs-boson search in top-quark decays~\cite{Aaboud:2017hnm}, which, on the other hand, is strongly sensitive to interference effects between signal and background and thus presents major experimental challenges.  In addition, this search is strongly motivated given the recent results obtained from the measurement of the \tttt~production cross-section 
which was measured to be $24^{+7}_{-6}$~fb for a Standard Model expectation of  $\sigma_{\tttt}=12.0\pm2.4$~fb~\cite{ATLAS:2021kqb}.   

The search targets a final state with one lepton or two leptons with opposite electric charge, and it uses all the data taken  in the full Run 2  with $pp$ collisions at $\sqrt{s} = 13$ TeV using an integrated luminosity of 139 $fb^{-1}$. The analysis uses Boosted Decision Trees (BDT) and a Graph Neural Network (GNN) to discriminate signal from the main background that originates from \ttbar+jets production. 
The modelling of the \ttbar+jets is studied in dedicated analysis regions and improved by a multivariate reweighting procedure; a neural network is used to obtain a multivariate probability density function that parametrise data/MC disagreement as a function of multiple kinematic quantities.   

