The Monte Carlo (MC) prediction of the nominal \ttbar + jets production samples (Powheg+Pythia8) up to six additional jets is not fully reliable. Therefore, data-based corrections, derived and applied before the fit to extract the signal, are a key ingredient in this analysis.

The two sources of mismodelling individually corrected by using data-driven correction factors. First, the rate of the \ttbar production in association with heavy-flavor jets (referred to as \ttbar +HF) is under-estimated, as observed by several previous searches and measurements. This is corrected by rescaling the normalization of each \ttbar +jets category based on the flavor of the extra jets, by comparing the yields of the data and the MC prediction in regions with different $b$-tagging requirements.

The jet multiplicity and the kinematic features of the additional jets are known to be mismodelled by the MC predictions at  multiplicity. A correction is then deployed by applying reweighting factors on the mismodelled observables, derived by comparing their distributions between the data and the MC prediction in the 2b region.
In this second step, a neural network-based approach is used to estimate the probability density functions of the data and the MC prediction, to derive reweighting factor as a ratio of them. This method allows to correct multiple observables at the same time, thus the MVA strategy used to define a signal-to-background discriminant has further flexibility on the input features choice as their modelling will typically be corrected.

%\subsection{\ttbar + jets truth classification}

\subsection{Flavor rescaling}
\label{sec:hf_rew}
\include{sections/sub_sec_HF_rew}


\clearpage
%%%%
\subsection{Neural-network based kinematic reweighting}
\label{sec:nn_rew}
\include{sections/sub_sec_NN_rew}
