\subsection{Changes between versions 0.6 and 0.7}

\begin{itemize}
  \item Fixed signal normalization (now it is normalized to 12 fb. Previously it was normalized to ${\sim}8$ fb.)
  \item Included high-pt b-tagging uncertainties in the fits.
  \item Added renormalization and factorization scale uncertainty for the signal samples.
  \item Changed the smoothing method for \ttbin modeling systematics (NLO matching, parton shower+haronization, 4FS) from ttbarresonances to maxVariation. Uptated red/blue plots are in Appendix \ref{app:TTB_modeling}. Added a new subsection with brief description of smoothing: Section \ref{sec:smoothing}.
  \item Unblinding was allowed:
  \begin{itemize}
    \item Added sections with unblinded data fits: Background-only in Section \ref{sec:unblinded_Bonly} and Signal+Background in Section \ref{sec:unblinded_SplusB})
    \item Added subsection comparing the three data fits (blinded, unblinded B-only, unblinded S+B): Section \ref{sec:fits_comparison}
    \item Added appendices with studies to understand unblinded fits, Appendix \ref{app:injection}, \ref{app:decorrelation_ttb_4FS}, and \ref{app:decorrelation_mu}.
  \end{itemize}
  \item Added section showing the combination with SSML channel (2HDM interpretation): Section \ref{sec:combination}
\end{itemize}


\subsection{Changes between versions 0.5 and 0.6}

\begin{itemize}
  \item Added clarification about wrong limits in figure \ref{sec:limits_data}.
  \item Updated the plots in Appendix M.1 to fulfill the blinding policy.
\end{itemize}



\subsection{Changes between versions 0.4 and 0.5}

\begin{itemize}
  \item Fixed a bug for the evaluation of the NN reweighting uncertainty using the dropout method (updated red/blue plots in Appendix E).
  \item Symmetrizing the non-ttbar normalization uncertainty in NN reweighting (this is to avoid underconstraint for this nuisance parameter which was observed in version 0.4).
  \item Added two new nuisance parameters for TTL normalization uncertainty ($5\%$) for 1L and 2L.
  \item Using Minos option in the fit for nuisance parameters ttbar\_reweighting\_1L,ttbar\_reweighting\_2L,NN\_reweighting\_nonttbarXS (this is to ensure any problems with underconstraint observed in version 0.4).
  \item Added a first version of the official high-pt PCB uncertainties from the Flavour Tagging group. Unfortunately the uncertainties are applied only to a subset of samples (this is because we are missing the jet true flavour). Removed the previous ad-hoc implementation of these uncertainties.
  \item Rerun all fit results with the above updates.
  \item Added red/blue plots for non-ttbar normalization uncertainty propagated via NN reweighting and red/blue plots for the NN reweighting uncertainty with the dropout method (Appendix E)
  \item Added red/blue plots with total MC vs Data comparison for the TTC normalization uncertainty (Appendix M.1)
  \item Added postfit Data/MC comparison for the variables used in the MVA training (Appendix L.2)
  \item Added distributions for the GNN input variables in the inclusive signal region with a cut on the GNN score to see where the signal is concentrated (Appendix O)
  \item Added prefit and postfit plots for mass points 700 GeV and 1000 GeV and also correlation matrices (Appendix P)
\end{itemize}




\subsection{Changes between versions 0.3 and 0.4}

\begin{itemize}
  \item Updated SM 4tops cross section and its uncertainty to use the latest prediction from Ref.~\cite{vanBeekveld:2022hty}.
  \item Updated V+jets cross section uncertainty to 60\% (previously used 40\%)
  \item Disabled smoothing for all weight systematics.
  \item Added one new nuisance parameter originating from the non-ttbar cross section uncertainty propagated via NN reweighting as described in Section \ref{sec:NN_reweighting:uncertainty}.
  \item Rerun all fit results with the above updates.
  \item Improved explanation of the MC dropout method in Section \ref{sec:NN_reweighting:uncertainty}.
  \item Checked the normalization changes after NN reweighting (Table \ref{tab:Rew_NoRew_YieldsRatio})
  \item Checked the HF SFs for ttbar modeling weight systemmatics (Appendix \ref{app:HFweights_weightSystematics}).
  \item Added prefit and postfit Data/Prediction plots for GNN input variables (Appendix \ref{app:validation_GNN_input_1L_ge10j4b} and \ref{app:validation_GNN_input_2L_ge8j3bL}).
  \item Added distributions before and after NN kinematic reweighting (Appendix \ref{app:NNRewPlots})
  \item Added Appendix \ref{app:TTC_pull} where the opposite pulls for ttc normalization between 1L and 2L is investigated.
\end{itemize}




\subsection{Changes between versions 0.1 and 0.2}

\begin{itemize}

\item \textbf{Included high-pt b-tagging uncertainties in the fit model}. using the same strategy as used in a similar analysis by Javier (TODO: add reference).

\item \textbf{Included ttbar kinematic reweighting uncertainty} -  (Section \ref{sec:NN_reweighting:uncertainty})

\item \textbf{Updated GNN plots} - The new GNN plots trained by using new samples including \texttt{``ATLAS work in progress''} label. See~\ref{sec:mva_gnn}).

\item \textbf{Included BDT vs GNN sensitivity comparison} - See Appendix~\ref{app:BDTvsGNN}.

\item \textbf{Included ttH and SM tttt generator uncertainties in the fit model}.

\item \textbf{Included 3-top samples among the background samples}. Also assigned normalization uncertainty for this sample.

\item \textbf{Extended Appendix~\ref{app:background_modeling_comp}  to illustrate data/MC agreements for all the features used in GNN}.

\item \textbf{Rerun all the fits with the above updates} - All the fit results are updated.

\item \textbf{Many small updates to address the comments received from the FAR review, see the comments on CDS.}

\end{itemize}
